\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{mlmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\input{glyphtounicode}
\pdfgentounicode=1

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\titleformat{\section}
  {\normalsize\bfseries\uppercase}
  {}
  {0pt}
  {}

\titlespacing*{\section}{0pt}{4pt}{1pt}
\setlist[itemize]{leftmargin=*, label={-}, itemsep=0pt, topsep=1pt, parsep=0pt, partopsep=0pt}

\begin{document}

% Header

{\LARGE \textbf{Rivaldo Silalahi}}\\[2pt]
\textit{Site Reliability Engineer | Kubernetes, Observability, Platform Engineering}\\[4pt]
Jakarta, Indonesia \quad|\quad
\href{mailto:rivaldosilalahi13@gmail.com}{rivaldosilalahi13@gmail.com} \quad|\quad
\href{tel:PHONE_NUMBER_PLACEHOLDER}{\texttt{\detokenize{PHONE_NUMBER_PLACEHOLDER}}} \quad|\quad
\href{https://www.linkedin.com/in/rivaldo-silalahi/}{linkedin.com/in/rivaldo-silalahi} \quad|\quad
\href{https://github.com/valdo766hi}{github.com/valdo766hi}

% Summary

\section*{Professional Summary}

Site Reliability Engineer with 4+ years of experience operating Kubernetes, observability, GitOps, and cloud infrastructure across AWS and GCP. Currently focused on production monitoring platforms, 99.99\% SLA/SLO workflows, infrastructure automation, and GPU/LLM infrastructure monitoring.

% Experience

\section*{Professional Experience}

\textbf{Lintasarta} - Senior Site Reliability Engineer \hfill Jul 2025-Present

\begin{itemize}[leftmargin=*]
  \item Standardized centralized observability using Cortex, ELK, and OpenTelemetry, defining shared dashboards, alerting patterns, and 99.99\% SLA/SLO views for multi-team operational use.
  \item Operated production k3s clusters for observability and shared platform services, improving reliability and day-2 operations for workloads aligned to 99.99\% SLA/SLO targets.
  \item Built Go-based exporters for NVIDIA GB200 BMC telemetry, exposing GPU health, capacity, and hardware metrics into Cortex/Prometheus for proactive infrastructure monitoring.
  \item Implemented GitOps workflows with Flux and Argo CD for dashboards, alerts, and configuration changes, making operational updates version-controlled, auditable, and reproducible.
  \item Improved incident triage by linking alerts, dashboards, and runbooks into a consistent observability workflow for platform and application teams.
  \item Collaborated with infrastructure and application teams to onboard services into centralized monitoring, reducing fragmented dashboards and duplicated alerting logic.
\end{itemize}

\textbf{GDP Labs} - Site Reliability Engineer \hfill Nov 2022-Jun 2025

\begin{itemize}[leftmargin=*]
  \item Provisioned AWS and GCP infrastructure with Terraform, Ansible, and Packer, delivering reproducible environments for internal platforms and client workloads.
  \item Operated Kubernetes platforms using EKS and Kubespray, supporting containerized microservices and shared platform components with production-readiness practices for 99.99\% SLA/SLO targets.
  \item Automated CI/CD workflows with Google Cloud Build and maintained deployment pipelines for application and infrastructure delivery.
  \item Managed monitoring and logging stacks with Prometheus, Grafana, and ELK, improving service visibility and incident troubleshooting workflows.
  \item Deployed GPU-based LLM inference workloads using vLLM and SGLang, validating throughput and latency behavior with k6 performance testing.
  \item Improved infrastructure maintainability by standardizing provisioning, deployment, and observability practices across cloud-native environments.
\end{itemize}

\textbf{GDP Labs} - Site Reliability Engineer Intern \hfill Jun 2022-Aug 2022

\begin{itemize}[leftmargin=*]
  \item Automated infrastructure provisioning with Terraform and Brainboard, and deployed VictoriaMetrics to support standardized monitoring environments.
\end{itemize}

\textbf{Generasi Gigih} - Backend Engineer Student \hfill Feb 2022-Jun 2022

\begin{itemize}[leftmargin=*]
  \item Completed backend engineering program using Ruby on Rails, TDD, and foundational system design.
\end{itemize}

\textbf{Finku} - DevOps Engineer Intern \hfill Oct 2021-Jan 2022

\begin{itemize}[leftmargin=*]
  \item Managed AWS cloud environments, built CircleCI pipelines, performed k6 API load testing, and created Grafana dashboards on Elasticsearch for backend service visibility.
\end{itemize}

% Education

\section*{Education}

Bachelor of Information Systems, Binus University \hfill 2024-2026\\
Associate Degree in Computer Technology, Del Institute of Technology \hfill 2019-2022


% Certifications

\section*{Certifications}

Certified Kubernetes Administrator (CKA) - Linux Foundation - \href{https://www.credly.com/badges/3e46e59e-33dc-4829-a42d-085a9e196dd8}{credly.com/badges/3e46e59e-33dc-4829-a42d-085a9e196dd8}

% Skills

\section*{Skills}

\textbf{Languages}: Go, Python, Bash, SQL, Nix\\
\textbf{Cloud \& Platforms}: AWS, GCP, Linux, NixOS, Kubernetes, EKS, k3s, Kubespray\\
\textbf{Observability}: Prometheus, Cortex, VictoriaMetrics, Grafana, ELK, Loki, OpenTelemetry, Alertmanager\\
\textbf{Infrastructure \& Delivery}: Terraform, Ansible, Packer, Helm, Docker, Flux, Argo CD, Google Cloud Build, CircleCI, GitHub Actions\\
\textbf{Performance \& AI Infrastructure}: k6, vLLM, SGLang, GPU monitoring

\end{document}
